---
title: "CPS Summary Statistics"
author: "Aaron R. Williams"
output: 
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(fig.width = 10)

```

```{css echo=FALSE}
h1 {
    font-size: 34px;
    color: #337AB7;
}

p {
    margin: 20px 0 20px;
}

```

# Preprocessing

```{r}
library(Hmisc)
library(tidyverse)
library(ipumsr)
library(reticulate)
library(janitor)
library(gt)
library(DT)

theme_set(theme_minimal())
theme_update(plot.title.position = "plot")

options(scipen = 999)

```

This codes loads the data from [IPUMS CPS](https://cps.ipums.org/cps/).

```{r}
ddi <- read_ipums_ddi(here::here("data", "cps_00008.xml"))
data <- read_ipums_micro(ddi)

```

# Counts

## No Noise

We reduce our sample to just heads of households and spouses.

```{r}
asec <- data %>%
  filter(ASECFLAG == 1) %>%
  filter(RELATE %in% c("101", "201"))

```

We count the unweighted and weighted observations.

```{r}
# unweighted observations
nrow(asec)

# weighted observations
sum(asec$ASECWT)

```

# Histograms

## No Noise -- Mortenson Figure 1

The Mortenson paper does not work with the CPS data because the data are rounded and imprecise. Still, we calculate a histogram for demonstration using five years of pooled CPS ASEC data.

```{r}
ddi <- read_ipums_ddi(here::here("data", "cps_00009.xml"))
cps_mort <- read_ipums_micro(ddi)

```

1. Load the CPS ASEC
2. Filter to where NCHILD == 2
3. Filter to where FILESTAT %in% c(4, 5)
4. Filter to drop dependents
5. Sum `INCWAGE`, `INCBUS`, and `INCFARM` to create earned income. 
6. Inflation adjust all years into 2014 dollars

```{r}
count(cps_mort, NCHILD)

eitc <- cps_mort %>%
  # limit to households with two children
  filter(NCHILD == 2) %>%
  # limit to single and head of household filers
  filter(FILESTAT %in% c(4, 5)) %>%
  # drop dependents
  filter(DEPSTAT == 0)

# calculate earned income
eitc <- eitc %>%
  mutate(
    earned_income = 
      INCWAGE +
      INCBUS +
      INCFARM
  )

# inflation adjust to 2014 dollars
eitc <- eitc %>%
  mutate(
    earned_income_2014 =
      case_when(
        YEAR == 2010 ~ earned_income * 236.715 / 218.076166666666,
        YEAR == 2011 ~ earned_income * 236.715 / 224.923,
        YEAR == 2012 ~ earned_income * 236.715 / 229.586083333333, 
        YEAR == 2013 ~ earned_income * 236.715 / 232.95175,
        YEAR == 2014 ~ earned_income
      )
  ) %>%
  select(earned_income, earned_income_2014)

eitc %>%
  filter(
    earned_income_2014 > 0,
    earned_income_2014 <= 30000
  ) %>%
  ggplot(aes(earned_income_2014)) +
  geom_histogram(binwidth = 1000) +
  scale_x_continuous(labels = scales::dollar) +
  labs(title = "Earned Income for Single/HOH Filers with 2 Child Dependents")

```

```{r}
source(here::here("R", "prep_cps03.R"))

mortenson_cps <- prep_cps03()

# values for specifications
breaks <- seq(from = 0, to = 30000, by = 1000)

# no noise ----------------------------------------------------------------
true_histogram <- hist(mortenson_cps$earned_income_2014, breaks = breaks, plot = FALSE)$counts

```

## Noisy Results

This table summarizes the results across all methods for histograms. Detailed data visualizations are in subsequent sections. 

```{r}
histogram_results <- read_csv(here::here("results", "03_cps_histograms.csv"), guess_max = 36000)

histogram_results <- histogram_results %>%
  mutate(
    relative_bias = bias /  mean(true_histogram)
  )

probs <- seq(0.1, 0.9, 0.1)

histogram_results_summary <- histogram_results %>%
  group_by(method, epsilon, delta) %>%
  summarize(
    q = probs, 
    relative_bias = quantile(relative_bias, probs = probs),
    bias = quantile(bias, probs = probs),
    rmse = quantile(rmse, probs = probs)
  ) %>%
  ungroup()

histogram_results_summary %>%
  filter(q == 0.5) %>%
  datatable()

```


```{r}
histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(q == 0.5,
         delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, relative_bias)) +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "Median Relative Bias for Income Histogram"
  )

histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         q %in% c(0.1, 0.5, 0.9)) %>%
  ggplot(aes(factor(epsilon), relative_bias)) +
  geom_line(aes(group = factor(q)), alpha = 0.2) +
  geom_point(aes(color = factor(q)), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "Relative Bias for Income Histogram",
    subtitle = "Selected percentiles"
  )

histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(q == 0.5,
         delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, bias)) +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "Median Bias for Income Histogram"
  )

histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         q %in% c(0.1, 0.5, 0.9)) %>%
  ggplot(aes(factor(epsilon), bias)) +
  geom_line(aes(group = factor(q)), alpha = 0.2) +
  geom_point(aes(color = factor(q)), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "Bias for Income Histogram",
    subtitle = "Selected Percentiles"
  )

histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(q == 0.5,
         delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, rmse)) +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method) +
  labs(
    title = "Median RMSE for Income Histogram"
  )

histogram_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         q %in% c(0.1, 0.5, 0.9)) %>%
  ggplot(aes(factor(epsilon), rmse)) +
  geom_line(aes(group = factor(q)), alpha = 0.2) +
  geom_point(aes(color = factor(q)), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "RMSE for Income Histogram",
    subtitle = "Selected Percentiles"
  )

```

# Mean Income

## No Noise

We calculate the unweighted and weighted mean of income from salaries and wages.

```{r}
# unweighted mean
true_mean_income <- mean(x = asec$INCWAGE)

# unweight CI
ci_length_original <- t.test(asec$INCWAGE)$conf.int[2] - t.test(asec$INCWAGE)$conf.int[1]

```

## Noisy Results

This table summarizes the results across all methods for means. 

```{r}
mean_income_results <- read_csv(here::here("results", "03_cps_mean-income.csv"), guess_max = 4500)

mean_income_results <- mean_income_results %>%
  mutate(
    noisy_mean = bias + true_mean_income,
    relative_bias = bias / true_mean_income#,
    #`Median Relative CI Length` = median(ci_length / ci_length_original)#,
  )

summary_mean_income_results <- mean_income_results %>%
  group_by(method, epsilon, delta) %>%
  summarize(
    `Median Relative Bias` = median(relative_bias), 
    RMSE = sqrt(mean(bias ^ 2)),
    `Median CI Overlap` = median(ci_overlap, na.rm = TRUE),
    `NAs in CI Overlap` = sum(is.na(ci_overlap)),
  ) %>%
  ungroup()

summary_mean_income_results %>%
  mutate(
    `Median Relative Bias` = round(`Median Relative Bias`, digits = 3),
    RMSE = round(RMSE, digits = 3),
    `Median CI Overlap` = round(`Median CI Overlap`, digits = 3),
    `NAs in CI Overlap` = round(`NAs in CI Overlap`, digits = 0)
  ) %>%
  datatable()

```

```{r}
summary_mean_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, `Median Relative Bias`)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "Median Relative Bias for Mean Income")

summary_mean_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, `Median CI Overlap`)) +
  geom_hline(yintercept = 1, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "CI Overlap for Mean Income")

summary_mean_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001)) %>%
  ggplot(aes(epsilon, RMSE)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "RMSE for Mean Income")

```

# Mean Earned Income

## No Noise

We calculate the unweighted and weighted mean of income from salaries and wages.

```{r}
# unweighted mean
true_mean_earned_income <- mean(x = eitc$earned_income_2014)

# unweighted CI
ci_length_original_earned <- t.test(eitc$earned_income_2014)$conf.int[2] - t.test(eitc$earned_income_2014)$conf.int[1]

```

## Noisy Results

This table summarizes the results across all methods for means. 

```{r}
mean_earned_income_results <- read_csv(here::here("results", "03_cps_mean-earned-income.csv"), guess_max = 10000)

mean_earned_income_results <- mean_earned_income_results %>%
  mutate(
    noisy_mean = bias + true_mean_income,
    relative_bias = bias / true_mean_income#,
    #`Median Relative CI Length` = median(ci_length / ci_length_original)#,
  )

summary_mean_earned_income_results <- mean_earned_income_results %>%
  group_by(method, epsilon, delta) %>%
  summarize(
    `Median Relative Bias` = median(relative_bias), 
    RMSE = sqrt(mean(bias ^ 2)),
    `Median CI Overlap` = median(ci_overlap, na.rm = TRUE),
    `NAs in CI Overlap` = sum(is.na(ci_overlap)),
  ) %>%
  ungroup()

summary_mean_income_results %>%
  mutate(
    `Median Relative Bias` = round(`Median Relative Bias`, digits = 3),
    RMSE = round(RMSE, digits = 3),
    `Median CI Overlap` = round(`Median CI Overlap`, digits = 3),
    `NAs in CI Overlap` = round(`NAs in CI Overlap`, digits = 0)
  ) %>%
  datatable()

```

```{r}
summary_mean_earned_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100) %>%
  ggplot(aes(epsilon, `Median Relative Bias`)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "Median Relative Bias for Mean Earned Income")

summary_mean_earned_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100) %>%
  ggplot(aes(epsilon, `Median CI Overlap`)) +
  geom_hline(yintercept = 1, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "CI Overlap for Mean Earned Income")

summary_mean_earned_income_results %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100) %>%
  ggplot(aes(epsilon, RMSE)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  labs(title = "RMSE for Mean Earned Income")

```

# Quantiles

## No Noise

We calculate unweighted and weighted percentiles of income from salaries and wages.

```{r}
percentiles <- seq(from = 0.1, to = 0.9, by = 0.1)

# unweighted percentiles
true_quantile <- quantile(x = asec$INCWAGE, probs = percentiles)

# weighted percentiles
wtd.quantile(x = asec$INCWAGE, weights = asec$ASECWT, probs = percentiles)

```

## Noisy Results {.tabset}

### With quantile_smooth

```{r}
quantile_results <- read_csv(here::here("results", "03_cps_quantiles.csv"))

quantile_results <- quantile_results %>%
  mutate(
    relative_bias =  bias / mean(true_quantile)
  )

quantile_results_summary <- quantile_results %>%
  group_by(method, epsilon, delta) %>%
  summarize(
    `Median bias` = median(bias),
    `Median relative bias` = median(relative_bias),
    RMSE = sqrt(mean(bias ^ 2))
    ) %>%
  ungroup()

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, `Median relative bias`)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +
  labs(
    title = "Median Relative Bias for Income Quantiles"
  )

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, `Median bias`)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +  
  labs(
    title = "Median Bias for Income Quantiles"
  )

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, RMSE)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method, scales = "free_y") +  
  labs(
    title = "RMSE for Income Quantiles"
  )

```

### Without quantile_smooth

```{r}
quantile_results_summary <- quantile_results_summary %>%
  filter(method != "quantile_smooth")

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, `Median relative bias`)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method) +
  labs(
    title = "Median Relative Bias for Income Quantiles"
  )

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, `Median bias`)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method) +  
  labs(
    title = "Median Bias for Income Quantiles"
  )

quantile_results_summary %>%
  filter(epsilon > 0.01) %>%
  filter(delta %in% c(NA, 0.000001),
         epsilon < 100,
         epsilon >= 0.1) %>%
  ggplot(aes(epsilon, RMSE)) +
  geom_hline(yintercept = 0, color = "red") +  
  geom_line(aes(group = method), alpha = 0.2) +
  geom_point(aes(color = method), alpha = 0.4) +
  facet_wrap(~method) +  
  labs(
    title = "RMSE for Income Quantiles"
  )

```


